Upper Limits on CN from Falling Evaporating Bodies\\seen towards \bp{}

### 2024-09-06 src/tex/ms.tex
CN limit figures

>>>>

\begin{figure}
    \begin{centering}
        \includegraphics[width=\columnwidth]{figures/HARPS_CN_stellar_frame.pdf}
        \caption{CN measurement limits in the stellar rest frame for a CN line width of 2.7\kms{}. Contours show signal to noise upper limits.}
        \label{fig:CN_stellar_frame}
        \script{plot_HARPS_CN_stellar_frame.py}
    \end{centering}
\end{figure}

\begin{figure*}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/HARPS_CN_exocomet_frame.pdf}
        \caption{CN measurement limits in the exocomet frame for a CN line width of 2.7, 10 and 20\kms{}. Contours show signal to noise upper limits.}
        \label{fig:CN_exocomet_frame}
        \script{plot_HARPS_CN_exocomet_frame.py}
    \end{centering}
\end{figure*}
